### 2021-05-14 docs/manuscript/PLOS-MSc-Thesis.tex
Relabel supplementary figures in order of appearance

These two events conduce to the repression of the gene C by the gene A in the
rightmost part of the morphogenetic field and by the morphogen in the leftmost
part of the morphogenetic field, thus generating a slightly higher level of
expression of gene C in the center of the field. Because gene C activates its
own expression, a band of expression begins to form. This band of expression
then begins to activate the gene A also in the center of the field
(\nameref{S2_Fig}).
% (Fig~\ref{fig:topol9-dyn}).

@@

\paragraph*{S1 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}
The dynamics of expression is shown from $t = 5$ to $t = 150$. The red line
represents the expression level of the gene C along the morphogenetic field,
whereas the dotted line represents the expression level of gene A. The
striped pattern of gene expression can be seen for both genes since $t = 80$.

\paragraph*{S2 Fig.}
\label{S3_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
expression profile (B).

\paragraph*{S3 Fig.}
\label{S4_Fig}
{\bf Bridge topologies in the neutral network.}

\paragraph*{S4 Fig.}
\label{S1_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}

>>>>

These two events conduce to the repression of the gene C by the gene A in the
rightmost part of the morphogenetic field and by the morphogen in the leftmost
part of the morphogenetic field, thus generating a slightly higher level of
expression of gene C in the center of the field. Because gene C activates its
own expression, a band of expression begins to form. This band of expression
then begins to activate the gene A also in the center of the field
(\nameref{S1_Fig}).
% (Fig~\ref{fig:topol9-dyn}).

@@

\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Dynamics of expression of topology number 9.}
The dynamics of expression is shown from $t = 5$ to $t = 150$. The red line
represents the expression level of the gene C along the morphogenetic field,
whereas the dotted line represents the expression level of gene A. The
striped pattern of gene expression can be seen for both genes since $t = 80$.

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
expression profile (B).

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Bridge topologies in the neutral network.}

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}
